---
title: "Cluster Metabolic analysis"
author: "TJ"
date: "5/14/2021"
output: pdf_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)
cluster1Metab <- read_csv("output/cluster1Metab.csv") # This is the arc/forearc
acluster3Metab <- read_csv("output/cluster3Metab.csv") # This is actually cluster 2 (Outer Forearc)
PrevalentMetab <- read_csv("output/PrevalentMetab.csv") # This is our prevalent group
```


# Forearc and Arc analysis: Cluster 1
```{r, echo=FALSE}
#### Forearc and Arc analysis (cluster 1) ####
metabol_list <- list("Iron Oxidation", "Nitrogen Oxidation",
                       "Hydrogen Oxidation", "Sulfur Oxidation*", 
                       "Sulfur Reduction",  "Nitrogen Reduction*",
                       "Iron Reduction", "Microaerobic", "Aerobic",
                       "CBB.present",  "CBB_FormI", "CBB_FormII", 
                       "CBB_FormI_and_II", "CBB_Form_Unknown", 
                       "rTCA.present", "Wood.Ljungdahl.present")   
```

## Total number of MAGs in Cluster 1
```{r, echo=FALSE}
print(paste("The total number of MAGs in the Forearc and Arc is", nrow(cluster1Metab)))
```


## Percent of total reads in that bined Cluster 1
```{r, echo=FALSE}
print(paste("The percent of total binned read found in the Forearc and Arc is",
            sum(cluster1Metab[,10:36])/sum(sum(cluster1Metab[,10:36]), sum(cluster3Metab[,10:36]), sum(PrevalentMetab[,10:36]))*100, "%"))
```

### Cluster 1: Percent of MAGs
```{r, echo=FALSE}
for (i in metabol_list){
  x <- nrow(subset(cluster1Metab, cluster1Metab[,i] >0))/nrow(cluster1Metab)*100
  print(paste(i, " is in", x, "% of the MAGs"))
}
```


### Cluster 1: Percent of reads
```{r, echo=FALSE}
for (i in metabol_list){
  x <- sum(subset(cluster1Metab, cluster1Metab[,i] >0)[,10:36])/sum(cluster1Metab[,10:36])*100
  print(paste(i, " is in", x, "% of the Reads"))
}
```


# Outer Forearc AnalysisOuter Forearc
```{r, echo=FALSE}
#### Outer forearc analysis (cluster 2) ####
library(tidyverse)

metabol_list <- list("Iron Oxidation", #"Nitrogen Oxidation",
                       "Hydrogen Oxidation", "Sulfur Oxidation*", 
                       "Sulfur Reduction",  "Nitrogen Reduction*",
                       "Iron Reduction", "Microaerobic", "Aerobic",
                       "CBB.present",  
                       "rTCA.present", "Wood.Ljungdahl.present") 
```


## Total number of MAGs in Outer Forearc
```{r, echo=FALSE}
print(paste("The total number of MAGs in the Outer forearc is", nrow(cluster3Metab)))

```


## Percent of total reads that bined in Outer Forearc
```{r, echo=FALSE}
print(paste("The percent of total binned read found in Outer Forearc is",
            sum(cluster3Metab[,10:36])/sum(sum(cluster1Metab[,10:36]), sum(cluster3Metab[,10:36]), sum(PrevalentMetab[,10:36]))*100, "%"))
```


### Outer Forearc: Percent of MAGs
```{r, echo=FALSE}
for (i in metabol_list){
  x <- nrow(subset(cluster3Metab, cluster3Metab[,i] >0))/nrow(cluster3Metab)*100
  print(paste(i, " is in", x, "% of the MAGs"))
}


```


### Outer Forearc: Percent of reads
```{r, echo=FALSE}
for (i in metabol_list){
  x <- sum(subset(cluster3Metab, cluster3Metab[,i] >0)[,10:36])/sum(cluster3Metab[,10:36])*100
  print(paste(i, " is in", x, "% of the Reads"))

```


# Prevalent: Prevalent
```{r, echo=FALSE}
#### Prevalent cluster 3 ###

metabol_list <- list("Iron Oxidation", "Nitrogen Oxidation",
                       "Hydrogen Oxidation", "Sulfur Oxidation*", 
                       "Sulfur Reduction",  "Nitrogen Reduction*",
                       "Iron Reduction", "Microaerobic", "Aerobic",
                       "CBB.present",  "CBB_FormI", "CBB_FormII", 
                       "CBB_FormI_and_II", "CBB_Form_Unknown", 
                       "rTCA.present", "Wood.Ljungdahl.present") 
```

## Total number of MAGs in Prevalent
```{r, echo=FALSE}
print(paste("The total number of MAGs in the Prevalent Community is", nrow(PrevalentMetab)))

```


## Percent of total reads that bined in Prevalent
```{r, echo=FALSE}
print(paste("The percent of total binned read found in the Prevalent community is",
            sum(PrevalentMetab[,10:36])/sum(sum(cluster1Metab[,10:36]), sum(cluster3Metab[,10:36]), sum(PrevalentMetab[,10:36]))*100, "%"))

```


### Prevalent: Percent MAGs
```{r, echo=FALSE}
for (i in metabol_list){
  x <- nrow(subset(PrevalentMetab, PrevalentMetab[,i] >0))/nrow(PrevalentMetab)*100
  print(paste(i, " is in", x, "% of the MAGs"))
}
```


### Prevalent: Percent reads
```{r, echo=FALSE}
for (i in metabol_list){
  x <- sum(subset(PrevalentMetab, PrevalentMetab[,i] >0)[,10:36])/sum(PrevalentMetab[,10:36])*100
  print(paste(i, " is in", x, "% of the Reads"))
}


```


### Forearc only
```{r, echo=FALSE}
forearc <-  new_cluster1 %>% subset(., select = c('bins','kingdom', 'phylum', 'class', 'order', 'family', 'genus', 'species',
                                                      'CYF', 'CYS', 'FAS','SLF', 'MTF', 'SLS', 'cluster')) %>%
  inner_join(., clean_metapath3[,-c(2:8)], by = "bins")

```

```{r, echo=FALSE}
metabol_list <- list("Iron Oxidation", "Nitrogen Oxidation",
                       "Hydrogen Oxidation", "Sulfur Oxidation*", 
                       "Sulfur Reduction",  "Nitrogen Reduction*",
                       "Iron Reduction", "Microaerobic", "Aerobic",
                       "CBB.present",  
                       "rTCA.present", "Wood.Ljungdahl.present") 
for (i in metabol_list){
  x <- sum(subset(forearc, forearc[,i] >0)[,9:14])/sum(forearc[,9:14])*100
  print(paste(i, " is in", x, "% of the Reads"))
}
```

### arc only
```{r, echo=FALSE}
arc <-  new_cluster1 %>% subset(., select = c('bins','kingdom', 'phylum', 'class', 'order', 'family', 'genus', 'species', 'BQS', 'BQF',
                                                  'BRF1', 'BRS2', 'BRF2', 'BRS1', 'ETS', 'QNF', 'QNS', 'RVF', 'TCF', 'TCS')) %>%
  inner_join(., clean_metapath3[,-c(2:8)], by = "bins")

```

```{r, echo=FALSE}
metabol_list <- list("Iron Oxidation", "Nitrogen Oxidation",
                       "Hydrogen Oxidation", "Sulfur Oxidation*", 
                       "Sulfur Reduction",  "Nitrogen Reduction*",
                       "Iron Reduction", "Microaerobic", "Aerobic",
                       "CBB.present",  
                       "rTCA.present", "Wood.Ljungdahl.present") 
for (i in metabol_list){
  x <- sum(subset(arc, arc[,i] >0)[,9:20])/sum(arc[,9:20])*100
  print(paste(i, " is in", x, "% of the Reads"))
}
```

```{r, echo=FALSE}
for (i in metabol_list){
  x <- nrow(subset(arc, arc[,i] >0))/nrow(arc)*100
  print(paste(i, " is in", x, "% of the MAGs"))
}

```


########################
# Aerobic MAGs with WL #
########################

```{r, echo=FALSE}
WLO2 <- bac_ko %>% subset(bins == "bin_377" | bins ==  "bin_237" |
                 bins == "bin_103" | bins == "bin_277" | 
                 bins == "bin_312" | bins == "bin_364" | 
                 bins == "bin_306"| bins == "bin_228" |
                 bins == "bin_368") %>% subset(ko == "K00404"| ko == "K02298")




```


#####
# Cyanobacteria (Phototroph)
####
# Percent of reads that mapped to phototrophs
```{r}
(sum(abun_py[abun_py$bins %in% c("bin_387", "bin_20", "bin_379", "bin_317"),][,15:41]))/sum(abun_py[,15:41])*100
```


```{r}
#outerinfo2
#ForearcArcinfo2
#arcinfo2
#prevalentinfo
print(paste(rowSums(cluster1Metab[cluster1Metab$phylum == 'Cyanobacteriota',][,10:38], na.rm = TRUE)/sum(sum(cluster1Metab[,10:38]))*100, "%"))
Cyanobac <- sum(subset(arc, arc[,i] >0)[,9:20])/sum(arc[,9:20])*100
print(paste(i, " is in", x, "% of the Reads"))

```










